A Review of Lossless Data Compression Algorithms

### 2020-04-25 paper.tex
readme update

\begin{abstract}

This work aims to provide an introduction to the domain of Data Compression in Information Theory and a comprehensive review of the existing literature in the field of algorithms for Lossless Data Compression. We identify and discuss the potential opportunities, barriers and the future scope of the field. We also review data compression methods used for text, image, video and  audio data.

%\subsection*{Results}
%Mostly about which algo performs best for what kinda field and all that. will write this later when the paper is complete. thats a reference example

\end{abstract}

@@

@@

\section{Conclusion}

@@

\begin{enumerate}
	\setcounter{enumi}{10}

>>>>

\begin{abstract}
This work aims to provide an introduction to the domain of Data Compression in Information Theory and a comprehensive review of the existing literature in the field of algorithms for Lossless Data Compression. We identify and discuss the potential opportunities, barriers and the future scope of the field. We also review data compression methods used for text, image, video and  audio data.
\end{abstract}

@@

\begin{center}
	\small{Submitted to \textbf{Dr. S.K.S. Parashar}}
\end{center}

@@

\section{Conclusion and Future Prospects}

In the presented review article we had an overview and simple examples of some of the most established methods in the domain of Lossless Data Compression. We also had a look at some of the modern research going on in the field. Almost every software system in function today has a component of compression and decompression to reduce the load and improve efficiency.

As we are moving towards a more data driven age, the amount of which users are creating data is exploding. In such scenarios, data compression stands at a very crucial juncture. Active research in this field will yield astonishing speed improvements in the current computing landscape.

\clearpage

@@

\begin{enumerate}
	\setcounter{enumi}{17}
